Accuracy and precision of zero-heat-flux temperature monitoring

### 2019-11-28 manuscript/manuscript.Rmd
column header removed for comparison

```{r table-1, layout="l-page-outset"}
ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- bind_rows(ma, .id="Comparison")
df %>% 
  rename("Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
    gt() %>% 
  tab_header(
    title = "Table 1. Results of meta-analyses"  )  %>% 
  tab_spanner(
    label = "Population limits of agreement",
    columns = vars(
      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
  )
```

>>>>

```{r table-1, layout="l-page-outset"}
ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- bind_rows(ma, .id="Comparison")
df %>% 
  rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
    gt() %>% 
  tab_header(
    title = "Table 1. Results of meta-analyses"  )  %>% 
  tab_spanner(
    label = "Population limits of agreement",
    columns = vars(
      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
  )
```
